\TheTitle

### 2017-06-15 paper/userstudy.tex
Commit selection description and figures

\begin{figure}[htpb]
  \centering
  \begin{tikzpicture}
    \begin{axis} [
      ylabel=Merges,
      xlabel=Total Commits,
      grid=both,
      legend pos = north west
      ]
      \addplot[chartred] table[x index=0, y index=5]\mergetable;
      \addlegendentry{Maximum}
      \addplot[chartyellow] table[x index=0, y index=6]\mergetable;
      \addlegendentry{Mean}
      \addplot[chartgreen] table[x index=0, y index=4]\mergetable;
      \addlegendentry{Median}
      \addplot[chartblue] table[x index=0, y index=3]\mergetable;
      \addlegendentry{Minimum}
    \end{axis}
  \end{tikzpicture}
  \caption{Number of merges versus the size of the merge tree}
  \label{fig:merge_count_filter}
\end{figure}

@@

We decided to work with one tree of one node, and one tree of seven
nodes.

>>>>

\begin{figure}[htpb]
  \centering
  \begin{tikzpicture}
    \begin{axis} [
      ylabel=Merges,
      xlabel=Total Commits,
      minor x tick num = 1,
      minor y tick num = 1,
      grid=both,
      legend pos = north west
      ]
      \addplot[chartred] table[x index=0, y index=5]\mergetable;
      \addlegendentry{Maximum}
      \addplot[chartyellow] table[x index=0, y index=6]\mergetable;
      \addlegendentry{Mean}
      \addplot[chartgreen] table[x index=0, y index=4]\mergetable;
      \addlegendentry{Median}
      \addplot[chartblue] table[x index=0, y index=3]\mergetable;
      \addlegendentry{Minimum}
    \end{axis}
  \end{tikzpicture}
  \caption{Number of merges versus the size of the merge tree}
  \label{fig:merge_count_filter}
\end{figure}

@@

As 25\% of the trees consist of a single commit, we selected one tree
consisting of a single commit for the study. 50\% of the trees contained
up to seven nodes, so we selected another tree of size seven.  Of these
trees, we restricted the selection to trees consisting of at least one
merge, not including the merge into the master branch.

From the list of trees consisting of a single node, we selected one at
random using a simple python script and the \verb|random.choice()|
function from python 3.6.1, which returned the merge tree rooted at
\emph{11df5864075f763ec0d1fdecd6a3f0af7d09a553}. As we are not testing
the inter-tree and tree-search capabilities of \emph{Linvis}, we start
the user at the corresponding commit. In this case, there is only a
single option, commit \emph{a3c1239eb59c0a907f8be5587d42e950f44543f8},
shown in Figure~\ref{fig:commit_1}.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.2\linewidth]{figures/commits/1-commit.pdf}
  \caption{The first merge tree used in the user study, a merge tree
    containing a single commit}
  \label{fig:commit_1}
\end{figure}

Using the same merge selection technique, we selected the tree rooted at
\emph{8eb88c80d444fd249edaa7d895666cde79e7b3b8}. To select the starting
commit, we use the python random choice function on the list of commit
hashes contained in this tree. This resulted in the selection of commit
\emph{cdbdd1676a5379f1d5cbd4d476f5e349f445befe}, shown in
Figure~\ref{fig:commit_2}.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.5\linewidth]{figures/commits/7-commits.pdf}
  \caption{The second merge tree used in the user study, a merge tree
    containing seven commits}
  \label{fig:commit_2}
\end{figure}
